Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/introduction.tex
Deleted some notes

% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}. Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}. Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a result of Bellman's curse of dimensionality. Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks. \dnote{Would prefer a different example} For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \enote{Cite Dabe Icaps}.

>>>>

% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}. Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}. Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a result of Bellman's curse of dimensionality. Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks. For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \cite{abel2015goal}.
